Understanding Factors That Affects the Existence of Digital Innovation Hubs

### 2024-12-01 paper/paper.qmd
Fixed Errors in Caption

```{r, fig.pos="H"}
#| label: fig-area-dih
#| tbl-cap: "Density of `area` Categorized by Presence of DIHs"
#| message: false
#| echo: false

@@

```{r, fig.pos="H"}
#| label: fig-parking-dih
#| tbl-cap: "Density of `parking` Categorized by Presence of DIHs"
#| message: false
#| echo: false

@@

```{r, fig.pos="H"}
#| label: fig-workstations-dih
#| tbl-cap: "Density of `workstations` Categorized by Presence of DIHs"
#| message: false
#| echo: false

@@

```{r, fig.pos="H"}
#| label: fig-year-dih
#| tbl-cap: "Density of `year` Categorized by Presence of DIHs"
#| message: false
#| echo: false

>>>>

```{r, fig.pos="H"}
#| label: fig-area-dih
#| fig-cap: "Density of `area` Categorized by Presence of DIHs"
#| message: false
#| echo: false

@@

```{r, fig.pos="H"}
#| label: fig-parking-dih
#| fig-cap: "Density of `parking` Categorized by Presence of DIHs"
#| message: false
#| echo: false

@@

```{r, fig.pos="H"}
#| label: fig-workstations-dih
#| fig-cap: "Density of `workstations` Categorized by Presence of DIHs"
#| message: false
#| echo: false

@@

```{r, fig.pos="H"}
#| label: fig-year-dih
#| fig-cap: "Density of `year` Categorized by Presence of DIHs"
#| message: false
#| echo: false
